Adolescent well-being in the digital age

### 2022-07-05 01-models.Rmd
Fix model equations

$$
\begin{align}
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\ 
&(\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i \\
&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model2}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions).

>>>>

$$
\begin{align}
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\ 
&(\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + \\
&\alpha_6 \text{Internet}^{\text{t-1[CB]}}_i
\\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model2}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions). $\text{Internet}^{\text{t-1[CB]}}_i$ are the between-country centered values.
